Methods

### 2019-01-21 Methods.Rmd
updated...

SACTN_split <- SACTN_monthly(df = SACTN_daily_temps_indexsplit)
save(SACTN_split, file = "SACTN_split.RData")
```

Find where different sites have overlapping time series within this `SACTN_daily_temps_indexsplit` dataset. A time series with a length of 3years is long enough.

@@

@@

OISSTDir <- "~/Documents/Masters_2019/MastersProject/Data"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))

>>>>

# SACTN_split <- SACTN_monthly(df = SACTN_daily_temps_indexsplit)
# save(SACTN_split, file = "SACTN_split.RData")
```

Find where different sites have overlapping time series within this `SACTN_split` dataset. A time series with a length of 3years is long enough. The only problem is that the SST data do not overlap during these years (1998, 1999, 2000)

@@

Here i am suppose to overlap the MUR data with the insitu collected data but the insitu collected data is from 199-2000
- find other overlapping more recent time with the in situ data?
-

@@

OISSTDir <- "~/Documents/Masters_2019/Data_SST"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))
